---
title: "Assignment03"
author: "Ted Kim"
date: "2022-09-16"
output:
  html_document:
    df_print: paged
  pdf_document: 
    latex_engine: xelatex
fontsize: 10pt
linestretch: 1.5
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE)
```

## Team Member
Seung Min Song

## Load library
```{r load-library, echo=TRUE}
library(tidyverse)
```

## 1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"
```{r get-college-majors, echo=TRUE}
url <- paste0(
        'https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/',
        'majors-list.csv'
       )
df <- read.csv(url)
```



### Find matched majors and display the results. \
The pattern to be used in the regular expression is defined as '**DATA|STATISTICS**' and the match is returned using the str_detect() function. Only values with *true* results are filtered from the data frame and displayed.
```{r find-only-major-matched}
#find only matched Major
regex1 = 'DATA|STATISTICS'
df %>%
  filter(str_detect(Major, regex1))
```



### Find matched majors, create new column using mutate and display the results. \
Using the lapply() and the str_detect() functions to store in a new field "is_include" whether the value in the major column of the data frame matches the pattern and display.
```{r using-mutate, echo=TRUE}

regex1 = 'DATA|STATISTICS'

df <- df %>%
        mutate(is_include = lapply(df$Major, function(str) {
                                  str_detect(str, regex1)
                                }))

#The following error occurred when trying to sort the column created using the lapply() 
#function.
#  unimplemented type 'list' in 'orderVector1'
#This is caused by the inclusion of a non-vector list in the data frame, which should be 
#converted to classical format using as.data.frame.

df2 <- as.data.frame(lapply(df, unlist))

print(df2[order(-df2$is_include), c('Major', 'is_include')], 
      row.names = FALSE, right = FALSE)

```


## 2 Write code that transforms the data below: \
[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange" \
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry" \
[9] "elderberry"   "lime"         "lychee"       "mulberry" \
[13] "olive"        "salal berry" \
\
Into a format like this: \
c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry",
  "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime",
  "lychee", "mulberry", "olive", "salal berry") \
\


### Define strings
```{r transforms-th-data, echo=TRUE}
str <- paste0('[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"', 
              '[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"',
              '[9] "elderberry"   "lime"         "lychee"       "mulberry"',
              '[13] "olive"        "salal berry"')
```



### Remove the most unnecessary characters first \
**[step 1] remove [:number]:whitespace and repeated :whitespaces** \
```{r step-1-u, echo=TRUE, tidy=TRUE, tidy.opts=list(width.cutoff=80)}
str1 <- str_replace_all(str, '\\[\\d+\\]\\s|\\s{2,}', '')
cat(str1)
```
\
   **[step 2] replace ""(no space) or " "(include space) to ", "** \
```{r step-2-u, echo=TRUE}
str1 <- str_replace_all(str1, '\\"\\s?\\"', '\\", \\"')
cat(str1)
```
\
   **[step 3] replace start of strings(line) " to c("** \
```{r step-3-u, echo=TRUE}
str1 <- str_replace_all(str1, '^\\"', 'c(\\"')
cat(str1)
```
\
   **[step 4] replace end of strings(line) " to ")** \
```{r step-4-u, echo=TRUE}
str1 <- str_replace_all(str1, '\\"$', '\\")')
cat(str1)
```
\
**[Wrap up]** \
wrap up step1 thru step4 above by combining them into one command 
```{r remove-unnecessary-first, echo=TRUE}
cat(str_replace_all(str, '\\[\\d+\\]\\s|\\s{2,}', '') %>%
      str_replace_all('\\"\\s?\\"', '\\", \\"') %>%
      str_replace_all('^\\"', 'c(\\"') %>%
      str_replace_all('\\"$', '\\")'))
```

### Replace string from left to right \
\
**[step 1] replace start of strings(line) [:number]:whitespace to c(** \
```{r echo=TRUE}
str2 <- str_replace_all(str, '^\\[\\d+\\]\\s', 'c(')
cat(str2)
```
\
**[step 2] replace white space(s) between double quotes such as "  " to ", "** \
```{r echo=TRUE}
str2 <- str_replace_all(str2, '\\"\\s+\\"', '\\", \\"')
cat(str2)
```
\
**[step 3] replace middle of strings(line) [:number]:whitespace to ', ' (comma & whitespace)** \
```{r echo=TRUE}
str2 <- str_replace_all(str2, '\\[\\d+\\]\\s+', ', ')
cat(str2)
```
\
**[step 4] replace end of strings(line) " to ") ** \
```{r echo=TRUE}
str2 <- str_replace_all(str2, '\\"$', '\\")')
cat(str2)
```
\
**[Wrap up]**\
wrap up step1 thru step4 above by combining them into one command 
```{r replace-string-left-right, echo=TRUE}
cat(str_replace_all(str, '^\\[\\d+\\]\\s', 'c(') %>%
      str_replace_all('\\"\\s+\\"', '\\", \\"') %>%
      str_replace_all('\\[\\d+\\]\\s+', ', ') %>%
      str_replace_all('\\"$', '\\")'))
``` 
\


###  String to Array \
Use the str_split() function to make a string array\
```{r string-to-array, echo=TRUE}
str1 <- str_replace_all(str, '\\[\\d+\\]\\s|\\s{2,}', '') %>%
       str_replace_all('\\"\\s?\\"', '\\", \\"')

print(str_split(str_replace_all(str1, '\\"', ''), ', ')[[1]])
```
\



## 3 Describe, in words, what these expressions will match:
```{r describe, echo=FALSE}
cat('(.)\\1\\1            : a capturing group of any character repeats three times in a row')
cat('(.)(.)\\2\\1         : Two capturing groups consisting of one character each and the next \n',
    '                    content of capturing are connected by the reverse order. \n',
    '                    Four letters are palindrome.')
cat('(..)\\1             : a capturing group of any two-characters repeats two times')
cat('(.).\\1.\\1          : A capturing group of any character is repeated three times. \n',
    '                    First, third, and fifth character shold be same, but second, and \n',
    '                    forth can be any other character. Furthermore, all five can be the \n',
    '                    same character.')
cat('(.)(.)(.).*\\3\\2\\1 : the first three any characters(capturing groups) and the last three \n',
    '                    characters as a palindrome')
```
\



## 4 Construct regular expressions to match words that:
### Define test strings
```{r define-arr, echo=TRUE}
arr <- c('church', 'buddy', 'tomato', 'eleven', 'bahama', 
         '12345612', '1234', 'seventeen', 'mom')
```


### Start and end with the same character.
```{r echo=TRUE}
# ^: start of string(line)
# $: end of string(line)
# .: any character except line break
# *: zero or more times
# (): capturing group
# \\1: contents of group 1
regex4_1 = '^(.).*\\1$'
str_detect(arr, regex4_1)
```

### Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r echo=TRUE}
# Start and end with the same (allow letter only)
# ^: start of string(line)
# $: end of string(line)
# [a-zA-Z]: only letter
# *: zero or more times
# (): capturing group
# \\1: contents of group 1
# {2}: exactly two times
regex4_2_1 = '^([a-zA-Z]{2})[a-zA-Z]*\\1$'
str_detect(arr, regex4_2_1)

# any position (allow letter only)
regex4_2_2 = '([a-zA-Z]{2})[a-zA-Z]*\\1'
str_detect(arr, regex4_2_2)

# Start and end with the same (allow any character)
regex4_2_3 = '^(.{2}).*\\1$'
str_detect(arr, regex4_2_3)

# any position (allow any character)
regex4_2_4 = '(.{2}).*\\1'
str_detect(arr, regex4_2_4)

```


### Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
```{r at-lease-three-places, echo=TRUE}
# *: zero or more times
# (): capturing group# 
# .: any character except line break
# \\1: contents of group 1
# {2}: exactly two times
regex4_3 = '(.).*\\1.*\\1'
str_detect(arr, regex4_3)

```

* [GitHub - https://github.com/blacksmilez/DATA607/tree/main/Assignment03](https://github.com/blacksmilez/DATA607/tree/main/Assignment03)
* RPubs - https://rpubs.com/blacksmilez/943744