---
title: "The Complete History Of The NBA Predictions"
author: "Ted Kim"
date: "2022-09-02"
output:
  pdf_document: default
  html_document:
    df_print: paged
linkcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

The complete history of the NBA [https://projects.fivethirtyeight.com/complete-history-of-the-nba/#warriors](https://projects.fivethirtyeight.com/complete-history-of-the-nba/#warriors) article is about Elo ratings for every NBA franchise - over 60,000 ratings in total. The article describes a simple formula for Elo rating calculation and the option to explore each and every NBA team's history. But they get more credit for upset victories and for winning by larger margins. Elo ratings are zero-sum, however. 

The article briefly talks about how dominant the 1990s Bulls were, the unbelievable 33 games winning streak by the 1971s Lakers, a strong but unacknowledged 60s Celtics, and the most brilliant season of the New York Knicks.

```{r}
  library(data.table)
  library(dplyr)

  nba_carmelo <- read.csv('https://raw.githubusercontent.com/blacksmilez/DATA607/0b1e776fb7bc21f3ad1e9b2b1e32818a78d92c8f/Assignment01/Data/nba_elo.csv') %>%
    mutate(
      team1 = as.factor(team1),
      team2 = as.factor(team2),
      playoff = ifelse(playoff == "f", 'FINAL', playoff),
      playoff = ifelse(playoff == "c", 'CONFERENCE FINAL', playoff),
      playoff = ifelse(playoff == "p", 'PLAY_IN ROUND', playoff),
      playoff = ifelse(playoff == "q", 'FIRST ROUND', playoff),
      playoff = ifelse(playoff == "s", 'PLAYOFFS', playoff),
      neutral = ifelse(neutral == 1, TRUE, FALSE)
    )
  nba_carmelo_final <- subset(nba_carmelo, season == 2018 & playoff == 'FINAL',
                              select=c('date','playoff','season','team1','team2',
                                       'score1','score2','elo1_pre','elo2_pre'))

  nba_carmelo_final
 ```
 
## Data frame for NBA_ELO
The data frame for NBA_ELO contains 20 variables. I have yet to think about which of these variables to take and discard. (*to be revised later*)
 
|Column Name    |Description                                                         |
|---------------|--------------------------------------------------------------------|
|date           |Date                                                                |
|season         |Season year, 1947-2022                                              |
|neutral        |TRUE if the game was played on neutral territory, FALSE if not      |
|playoff        |TRUE if the game was a playoff game, FALSE if not                   |
|team1          |The name of one participating team                                  |
|team2          |The name of the other participating team                            |
|elo1_pre       |Team 1's Elo rating before the game                                 |
|elo2_pre       |Team 2's Elo rating before the game                                 |
|elo_prob1      |Team 1's probability of winning based on Elo rating                 |
|elo_prob2      |Team 2's probability of winning based on Elo rating                 |
|elo1_post      |Team 1's Elo rating after the game                                  |
|elo2_post      |Team 2's Elo rating after the game                                  |
|carmelo1_pre   |Team 1's CARMELO rating before the game                             |
|carmelo2_pre   |Team 2's CARMELO rating before the game                             |
|carmelo1_post  |Team 1's CARMELO rating after the game                              |
|carmelo2_post  |Team 2's CARMELO rating after the game                              |
|carmelo_prob1  |Team 1's probability winning based on CARMELO rating                |
|carmelo_prob2  |Team 2's probability of winning based on CARMELO rating             |
|score1         |Points scored by Team 1                                             |
|score2         |Points scored by Team 2                                             |

## Conclusion
*to be revised later*
 
 
* GitHub - https://github.com/blacksmilez/DATA607/tree/main/Assignment01
* RPubs - https://rpubs.com/blacksmilez/938241
